---
title: "SI_quant"
output: html_document
---
Horowitz, Mekler, Schneider, Frank, etc. 
Analyses for Scalar Implicature, Give-Quantifier, and DCCS


Set up Rmd parameters
```{r}
library(knitr)
opts_chunk$set(cache=TRUE, message=FALSE, warning=FALSE)
```

Preliminaries
```{r}
rm(list=ls())
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(stringr)
library(tidyr)
library(markdown)
library(directlabels)
library(magrittr)
library(bootstrap)
library(RCurl)


theme_set(theme_bw())
```

FIRST, visualize all the results, split by task

SI data setup
```{r}
#reading in the original wide-form dataframe
d1 <- read.csv("../data/SI_coding.csv")

#fill in the selection types for easier analyses
d1 %<>%
  mutate(carrot_selection = factor(carrot_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")), 
         hat_selection = factor(hat_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         cookies_selection = factor(cookies_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         trains_selection = factor(trains_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         cats_selection = factor(cats_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")),
         purses_selection = factor(purses_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         keys_selection = factor(keys_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         shirts_selection = factor(shirts_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")),
         breads_selection = factor(breads_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         horses_selection = factor(horses_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         bears_selection= factor(bears_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         frogs_selection = factor(frogs_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         plates_selection = factor(plates_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         books_selection = factor(books_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         elephants_selection = factor(elephants_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")),
         lamps_selection = factor(lamps_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         bananas_selection = factor(bananas_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")), 
         butterflies_selection = factor(butterflies_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")))

d2=melt.data.frame(d1,c("sub_ID","test_age", "order", "training"),c("carrot", "hat", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", "carrot_selection", "hat_selection", "cookies_selection", "trains_selection", "cats_selection", "purses_selection",  "keys_selection", "shirts_selection", "breads_selection", "horses_selection", "bears_selection", "frogs_selection", "plates_selection", "books_selection", "elephants_selection", "lamps_selection", "bananas_selection", "butterflies_selection", "carrot_type", "hat_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))


#making a respectable df  
onethird <- (1/3)*nrow(d2)
data <- d2[1:onethird,]
data$selection <- d2$value[(onethird+1):(onethird*2)]
data$type <- d2$value[(2*onethird+1):nrow(d2)]
names(data)[5] <- "item"
names(data)[6] <- "SI_correct"
data$correct <- data$SI_correct==1

#filtering out NAs, adding agesplit
data %<>%
  filter(sub_ID != "", correct != "NA") %>%
  mutate(agesplit = cut(test_age, breaks=c(3, 3.5, 4, 4.5, 5)), 
         agesplit = factor(agesplit,
                           labels=c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years"))) %>%
  filter(agesplit != "NA")

#renaming for better-looking graphs
data$type %<>%
  str_replace("control_all", "All")%>%
  str_replace("control_none", "None")%>%
  str_replace("implicature", "Implicature")

data$selection %<>%
  str_replace("all", "All")%>%
  str_replace("none", "None")%>%
  str_replace("some", "Some")

#Find the Mean and median ages
age <- data %>%
  dplyr::select(sub_ID, test_age, agesplit) %>%
  dplyr::distinct() %>%
  group_by(agesplit)%>%
  summarise(n=n(), avg = mean(test_age))

#use this dataframe for stats
data_si <- data %>%
  mutate(test = "Scalar Implicature")
```


SI graphs
```{r}
#number of kids in each age group
num_kids <- data %>%
  dplyr::select(sub_ID, agesplit) %>%
  dplyr::distinct() %>%
  dplyr::group_by(agesplit)%>%
  dplyr::summarize(n=n())

#accuracy by age group in different trials 
agg.data <- aggregate(data$correct, list(data$type, data$agesplit), FUN=sum)
agg.data.len <- aggregate(data$correct, list(data$type, data$agesplit), FUN=length)
agg.data$x <- agg.data$x 
agg.data.len$x <- agg.data.len$x 

names(agg.data) <- c("type", "Agesplit", "correct")
agg.data$total <- agg.data.len$x
agg.data$prop.corr <- agg.data$correct / agg.data$total

#prop correct and standard error
agg.data$q <- 1 - agg.data$prop.corr
agg.data$err <- sqrt((agg.data$prop.corr * agg.data$q) / agg.data$total)

#defining variables
dodge <- position_dodge(width=0.9) 
limits <- aes(ymax = prop.corr + err, ymin=prop.corr - err) 

#plot
quartz()
ggplot(data = agg.data, 
       aes(x=type, y=prop.corr, fill=Agesplit)) +
  geom_bar(stat="identity", position = position_dodge())  + geom_errorbar(limits, position=dodge)+
  ylab("Proportion correct") + 
  xlab("Trial Type") +
  scale_fill_brewer(palette="Set1")
```

Okay, what kinds of items are choosing on trials when they get things wrong?
```{r}
#first, filter out trials where kids got things right
si_wrong <- data %>%
  filter(SI_correct != 1, type != "All") %>%
  group_by(agesplit, type, selection)%>%
  dplyr::summarise(n=n())%>%
  dplyr::rename(Agesplit = agesplit) %>%
  mutate(n.total = sum(n), prop = n/n.total)

#now graph
quartz()
ggplot(data = si_wrong, 
       aes(x=selection, y=n, fill=Agesplit)) +
  geom_bar(stat="identity", position = position_dodge())  +
  ylab("Count of children choosing in trial") + 
  xlab("Selection Type") + facet_wrap(~type) +
  scale_fill_brewer(palette="Set1")
  
```


GQ data setup
```{r}
#read in and establish dataframe
d1 <- read.csv("../data/GQ_coding.csv")
d1[,c(8,10,12,14,16,18,20,22, 31, 32, 33, 34)] <- sapply(d1[,c(8,10,12,14,16,18,20,22, 31, 32, 33, 34)],as.character) #for unknown reasons this is necessary for melt.data.frame now

#change to long form
d2=melt.data.frame(d1,c("sub_ID", "test_age","condition", "order", "training"),c("X1_condition", "X2_condition", "X3_condition", "X4_condition", "X5_condition", "X6_condition",  "X7_condition", "X8_condition", "X1_given", "X2_given", "X3_given", "X4_given", "X5_given", "X6_given",  "X7_given", "X8_given", "X1_correct", "X2_correct", "X3_correct", "X4_correct", "X5_correct", "X6_correct",  "X7_correct", "X8_correct"))

#making a respectable df  
onethird <- (1/3)*nrow(d2)
data <- d2[1:onethird,]
data$selection <- d2$value[(onethird+1):(onethird*2)]
data$type <- d2$value[(2*onethird+1):nrow(d2)]
names(data)[6] <- "trial"
names(data)[7] <- "prompt"
names(data)[8] <- "num_given"
names(data)[9] <- "GQ_correct"

#filtering data, creating age breaks
data %<>%
  filter(sub_ID != "", num_given != "N/A") %>%
  mutate(split_2 = cut(test_age, breaks=c(3, 4, 5)), 
         Agesplit = factor(split_2,
                           labels=c("3-4 years", "4-5 years"))) %>%
  filter(Agesplit != "NA", num_given != "0 (8 oranges)", num_given != "0 (8 bananas)", num_given != "0 (8 strawberries)")

#this is because num_given is a factor - need to change to a number - need to do this for standard error
data$num_given <- as.character(data$num_given)
data$num_given <- as.numeric(data$num_given)
data$GQ_correct <-as.character(data$GQ_correct)
data$GQ_correct <- as.numeric(data$GQ_correct)

#renaming things for prettier graphs
data$prompt %<>%
  str_replace("all", "All")%>%
  str_replace("most", "Most")%>%
  str_replace("some", "Some")%>%
  str_replace("none", "None")

#creating dataframe for analyses
data_gq <- data %>%
  mutate(test = "Give-Quantifier")
```

Average given for each prompt by age group - this is not an informative graph, but is nice to have
```{r}
agg.data <- aggregate(data$num_given, list(data$prompt, data$Agesplit), FUN=mean)
agg.data.sd <- aggregate(data$num_given, list(data$prompt, data$Agesplit), FUN=sd)

names(agg.data) <- c("prompt", "Agesplit", "num_given")
agg.data$sd <- agg.data.sd$x

##establish limits
limits <- aes(ymax = num_given + sd, ymin=num_given - sd) 

#plot
quartz()
ggplot(data = agg.data, 
       aes(x=prompt, y=num_given, fill=Agesplit)) +
  geom_bar(stat="identity", position = position_dodge())  + geom_errorbar(limits, position=dodge)+
  ylab("Mean number given") + 
  xlab("Quantifier prompt") +
  scale_fill_brewer(palette="Set1")
```

Correct trials split by age - note, this is just whether kids got the trial correct or not
```{r}
agg.data <- aggregate(data$GQ_correct, list(data$prompt, data$Agesplit), FUN=sum)
agg.data.len <- aggregate(data$GQ_correct, list(data$prompt, data$Agesplit), FUN=length)
agg.data$x <- agg.data$x 
agg.data.len$x <- agg.data.len$x 

names(agg.data) <- c("prompt", "Agesplit", "correct")
agg.data$total <- agg.data.len$x
agg.data$prop.corr <- agg.data$correct / agg.data$total

#prop correct and standard error
agg.data$q <- 1 - agg.data$prop.corr
agg.data$err <- sqrt((agg.data$prop.corr * agg.data$q) / agg.data$total)

#defining variables
dodge <- position_dodge(width=0.9) 
limits <- aes(ymax = prop.corr + err, ymin=prop.corr - err) 

#plot
quartz()
ggplot(data = agg.data, 
       aes(x=prompt, y=prop.corr, fill=Agesplit)) +
  geom_bar(stat="identity", position = position_dodge())  + geom_errorbar(limits, position=dodge)+
  ylab("Proportion Correct") + 
  xlab("Quantifier Prompt") +
  scale_fill_brewer(palette="Set1")

```


Number given (average) Split by four age groups:
```{r}
hist_data <- data %>%
  group_by(Agesplit, prompt, num_given)%>%
  dplyr::summarise(n = n()) %>%
  group_by(Agesplit, prompt) %>%
  mutate(n.total = sum(n), prop = n/n.total)

hist1 <- hist_data %>%
  filter(prompt != "Most")

#plot
quartz()
ggplot(data = hist1, aes(x = num_given, y = prop, fill = Agesplit)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  xlab("Number Given") +
  ylab("Proportion of children giving in trial") + 
  scale_fill_brewer(palette="Set1") + facet_wrap(Agesplit ~ prompt, ncol = 3) 
```


DCCS data setup
```{r}
#wide-form
d1 <- read.csv("../data/DCCS_coding.csv")
#long form
d2=melt.data.frame(d1,c("sub_ID","test_age","condition", "order"),c("pre_1", "pre_2", "pre_3", "pre_4", "pre_5", "pre_6",  "post_1", "post_2", "post_3", "post_4", "post_5", "post_6"))

#filtering data, creating age breaks
data <- d2 %>%
  filter(sub_ID != "") %>%
  mutate(agesplit = cut(test_age, breaks=c(3, 3.5, 4, 4.5, 5)), 
         agesplit = factor(agesplit,labels=c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years")))

#renaming things
names(data)[5] <- "trial_type"
names(data)[6] <- "DCCS_correct"

#df for further analyses
data_dccs <- data
data_dccs$test <- "DCCS"
  
```

More sensible DCCS graph with collapsed "pre" and "post" switch trials
```{r}
tmp1 <- unlist(data$trial_type)%>%
  str_replace("pre_1", "pre")%>%
  str_replace("pre_2", "pre")%>%
  str_replace("pre_3", "pre")%>%
  str_replace("pre_4", "pre")%>%
  str_replace("pre_5", "pre")%>%
  str_replace("pre_6", "pre")%>%
  str_replace("post_1", "post")%>%
  str_replace("post_2", "post")%>%
  str_replace("post_3", "post")%>%
  str_replace("post_4", "post")%>%
  str_replace("post_5", "post")%>%
  str_replace("post_6", "post")

tmp <- as.data.frame(tmp1) %>%
  dplyr::rename(switch_type = tmp1)
tmp2 <- bind_cols(data, tmp)
data <- tmp2

#renaming for prettier graphs
data$switch_type %<>%
  str_replace("post", "Post-switch")%>%
  str_replace("pre", "Pre-switch")

data$switch_type <- as.factor(data$switch_type)
```


Accuracy on DCCS task
```{r}
#aggregate correct by trial type and age
agg.data <- aggregate(data$DCCS_correct, list(data$switch_type, data$agesplit), FUN=sum)
agg.data.len <- aggregate(data$DCCS_correct, list(data$switch_type, data$agesplit), FUN=length)
agg.data$x <- agg.data$x 
agg.data.len$x <- agg.data.len$x 

names(agg.data) <- c("trial_type", "Agesplit", "correct")
agg.data$total <- agg.data.len$x
agg.data$prop.corr <- agg.data$correct / agg.data$total

#standard error
agg.data$q <- 1 - agg.data$prop.corr
agg.data$err <- sqrt((agg.data$prop.corr * agg.data$q) / agg.data$total)

#variables established
dodge <- position_dodge(width=0.9) 
limits <- aes(ymax = prop.corr + err, ymin=prop.corr - err) 

a <- agg.data
a$trial_type <- factor(a$trial_type, levels=c("Pre-switch","Post-switch"))

#plot
quartz()
ggplot(data = a, 
       aes(x=trial_type, y=prop.corr, fill=Agesplit)) +
  geom_bar(stat="identity", position = position_dodge())  + geom_errorbar(limits, position=dodge)+
  ylab("Proportion Correct") + 
  xlab("Trial Type") +
  scale_fill_brewer(palette="Set1")
```


STATS

Before we do anything else, read in Ali's data - we want to know if her data is significantly different than ours
```{r}
ali_si <- read.csv("../data/implicatures_scalarOnly_data.csv")

#manipulate data to look more like ours
d2=melt.data.frame(ali_si,c("Subj_ID","age","agegroup","list"),c("carrots", "hats", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", 
"carrots_selectionType", "hats_selectionType", "cookies_selectionType", "trains_selectionType", "cats_selectionType", "purses_selectionType",  "keys_selectionType", "shirts_selectionType", "breads_selectionType", "horses_selectionType", "bears_selectionType", "frogs_selectionType", "plates_selectionType", "books_selectionType", "elephants_selectionType", "lamps_selectionType", "bananas_selectionType", "butterflies_selectionType", 
"carrots_type", "hats_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))


data_ali <- d2[1:918,] 
data_ali$selectionType <- d2$value[919:1836]
data_ali$type <- d2$value[1837:2754]
names(data_ali)[5] <- "item"
names(data_ali)[6] <- "correct"

data_ali %<>%
  filter(Subj_ID != "", correct != "NA") %>%
  mutate(agesplit = cut(age, breaks=c(3, 3.5, 4, 4.5, 5)), agesplit = factor(agesplit,
                           labels=c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years"))) %>%
  filter(agesplit != "NA")

data_ali$correct <- as.character(data_ali$correct)
data_ali$correct <- as.numeric(data_ali$correct)

```

Summary measures for each participant with Ali's data
```{r}
#scalar implicature task
mss <- data_ali %>%
  group_by(Subj_ID, type)%>%
  dplyr::summarise(correct=mean(correct),
                   age = age[1], 
                   agesplit = agesplit[1])%>%
  spread(type, correct)
```

Read in our SI data, create a summary measure per participant
```{r}
#si df
data_si$SI_correct <- as.character(data_si$SI_correct)
data_si$SI_correct <- as.numeric(data_si$SI_correct)

#scalar implicature task
mss.acc <- data_si %>%
  group_by(sub_ID, type)%>%
  dplyr::summarise(correct=mean(SI_correct), 
                   test_age = test_age[1])%>%
  spread(type, correct)
```

Check if Ali's results are statistically different than ours - just a quick independent sample t-test
```{r}
#resample our data to get the sample sizes equal - ideally we should repeat this a bunch
si.x <- sample_n(mss.acc, 51)

#then, add her data to ours to do test
d.combined <- bind_cols(si.x, mss)

#weird number transformation
d.combined$age <- as.character(d.combined$age)
d.combined$age <- as.numeric(d.combined$age)

d.combined$test_age <- as.character(d.combined$test_age)
d.combined$test_age <- as.numeric(d.combined$test_age)

#the t test for implicature performance in general
with(d.combined, t.test(Implicature,some,equal.var=TRUE))

#what about by age?
d.1 <- d.combined %>%
  filter(age < 3.5 | test_age < 3.5)
with(d.1, t.test(Implicature,some,equal.var=TRUE))

d.2 <- d.combined %>%
  filter(age < 4 & age > 3.5 | test_age < 4 & test_age > 3.5)
with(d.2, t.test(Implicature,some,equal.var=TRUE))

d.3 <- d.combined %>%
  filter(age < 4.5 & age > 4 | test_age < 4.5 & test_age > 4)
with(d.3, t.test(Implicature,some,equal.var=TRUE))

d.4 <- d.combined %>%
  filter(age < 5 & age > 4.5 | test_age < 5 & test_age > 4.5)
with(d.4, t.test(Implicature,some,equal.var=TRUE))


#performance on none trials, same
with(d.1, t.test(None,none,equal.var=TRUE))
with(d.2, t.test(None,none,equal.var=TRUE))
with(d.3, t.test(None,none,equal.var=TRUE))
with(d.4, t.test(None,none,equal.var=TRUE))
```


Now DCCS
```{r}
#this is a terrible and horrible thing that I had to do in order to get the data formatted correctly
tmp1 <- unlist(data_dccs$trial_type)%>%
  str_replace("pre_1", "pre")%>%
  str_replace("pre_2", "pre")%>%
  str_replace("pre_3", "pre")%>%
  str_replace("pre_4", "pre")%>%
  str_replace("pre_5", "pre")%>%
  str_replace("pre_6", "pre")%>%
  str_replace("post_1", "post")%>%
  str_replace("post_2", "post")%>%
  str_replace("post_3", "post")%>%
  str_replace("post_4", "post")%>%
  str_replace("post_5", "post")%>%
  str_replace("post_6", "post")

#seriously, this is so terrible
tmp <- as.data.frame(tmp1) %>%
  dplyr::rename(switch_type = tmp1)
tmp2 <- bind_cols(data_dccs, tmp)
data_dccs <- tmp2

```

```{r}
#dccs task summary measures by participant
mss.acc2 <- data_dccs %>%
  group_by(sub_ID, switch_type)%>%
  dplyr::summarise(correct=mean(DCCS_correct))%>%
  spread(switch_type, correct)
```

Now GQ
```{r}
#gq task - note that some of these are NAs because the kids gave 0 of the named fruit, but 8 of another fruit
#first mean number
mss.acc3 <- data_gq %>%
  group_by(sub_ID, prompt)%>%
  dplyr::summarise(mean_num = mean(num_given)) %>%
  spread(prompt, mean_num)

#then correct
mss.acc4 <- data_gq %>%
  group_by(sub_ID, prompt)%>%
  dplyr::summarise(mean_correct = mean(GQ_correct))%>%
  spread(prompt, mean_correct)
```

Create a wide-form df on which to run analyses - note that these are the mean performances across all trials per participant
```{r}
#this is joining the summary measures we created above, and renaming the variables so that we keep everything straight
tmp <- right_join(mss.acc, mss.acc2, by = "sub_ID")
tmp1 <- right_join(tmp, mss.acc3, by = "sub_ID") 
d_all <- right_join(tmp1, mss.acc4, by = "sub_ID") %>%
  dplyr::rename(SI_none = None.x, 
         SI_all = All.x, 
         SI_implicature = Implicature, 
         DCCS_post = post, DCCS_pre = pre, 
         GQ_all = All.y, 
         GQ_most = Most.x, 
         GQ_some = Some.x, 
         GQ_none = None.y, 
         GQ_all_correct = All, 
         GQ_most_correct = Most.y, 
         GQ_some_correct = Some.y, 
         GQ_none_correct = None,
         test_age = test_age)
```


CORRELATIONS

First make a huge correlation matrix of all variables
```{r}
source("ggcorplot.R")

d_all$GQ_none[is.na(d_all$GQ_none)] <- 0 # backfill when they gave the wrong object (but none of the target)
cor.data <- d_all %>%
  dplyr::select(-sub_ID, -GQ_all, -DCCS_pre) %>%
  filter(complete.cases(.)) %>%
  data.frame

quartz()
ggcorplot(data=cor.data)
```

Correlation between age and DCCS post
```{r}
#significant correlation between age and DCCS post performance
cor.test(d_all$test_age, d_all$DCCS_post)
```

Partial correlations - control for age
First, Scalar Implicature with DCCS and SI
```{r}
library(ppcor)
#partial correlation - implicature and dccs
#NS
pcor.test(d_all$SI_implicature, d_all$DCCS_post, d_all$test_age)

#Significant correlation between performance on implicature and none trials in SI task after controlling for age
pcor.test(d_all$SI_implicature, d_all$SI_none, d_all$test_age)

#NS
pcor.test(d_all$SI_none, d_all$DCCS_post, d_all$test_age)
```

Then GQ with DCCS and GQ
```{r}
#NS
pcor.test(d_all$GQ_none, d_all$DCCS_post, d_all$test_age)
#NS
pcor.test(d_all$GQ_some, d_all$DCCS_post, d_all$test_age)

#highly significant correlation between performance on GQ none and some trials, controlling for age
pcor.test(d_all$GQ_none, d_all$GQ_some, d_all$test_age)

```

Finally GQ with SI
```{r}
#NS
pcor.test(d_all$SI_implicature, d_all$GQ_some, d_all$test_age)

#almost signficant negative correlation between SI_none performance and GQ_some, controlling for age. This means that kids who do worse on the SI_none tasks are more likely to give more items for GQ_some (aka give 8 items for some)
pcor.test(d_all$SI_none, d_all$GQ_some, d_all$test_age)

#NS
pcor.test(d_all$SI_implicature, d_all$GQ_none, d_all$test_age)

#very significant negative correlation between performance on SI_none and GQ_none, meaning that kids who do worse on SI_none are more likely to give all 8 objects for none
pcor.test(d_all$SI_none, d_all$GQ_none, d_all$test_age)

```

What about when GQ is scored as correct/incorrect?
Partial correlations for GQ_correct with everything
```{r}
#first scalar implicature

#significant correlation between getting GQ some and SI implicature trials correct
pcor.test(d_all$GQ_some_correct, d_all$SI_implicature, d_all$test_age)

#significant correlation between getting GQ none and SI none correct
pcor.test(d_all$GQ_none_correct, d_all$SI_none, d_all$test_age)

#significant between GQ some and SI none
pcor.test(d_all$GQ_some_correct, d_all$SI_none, d_all$test_age)
 

#NS 
pcor.test(d_all$SI_implicature, d_all$GQ_none_correct, d_all$test_age)

#now DCCS
#NS
pcor.test(d_all$GQ_some_correct, d_all$DCCS_post, d_all$test_age)
#NS
pcor.test(d_all$GQ_none_correct, d_all$DCCS_post, d_all$test_age)
```

GRAPHS

```{r}
#add agesplit to large dataframe to make correlation graphs
d_all %<>%
  mutate(Agesplit = cut(test_age, breaks=c(3, 3.5, 4, 4.5, 5)), 
         Agesplit = factor(Agesplit,labels=c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years")))

#SI none and SI implicature
quartz()
ggplot(d_all, aes(x=SI_none, y=SI_implicature, colour=Agesplit)) + 
  geom_point(stat = "identity", position = position_jitter(.001), shape=16) + 
  geom_smooth(method="lm", col="black", lty=1) + 
  geom_smooth(aes(col=Agesplit, group=Agesplit), 
				se=FALSE, method="lm",lty=3) + 
  scale_colour_brewer(palette="Set1") + 
  labs(x = "Proportion of SI 'none' trials correct", y = "Proportion of SI 'implicature' trials correct")

#GQ some and SI none
quartz()
ggplot(d_all, aes(x=GQ_some_correct, y=SI_none, colour=Agesplit)) + 
  geom_point(stat = "identity", position = position_jitter(.001), shape=16) + 
  geom_smooth(method="lm", col="black", lty=1) + 
  geom_smooth(aes(col=Agesplit, group=Agesplit), 
				se=FALSE, method="lm",lty=3) + 
  scale_colour_brewer(palette="Set1") + 
  labs(y = "Proportion of SI 'none' trials correct", x = "Proportion of GQ 'some' trials correct")

#GQsome and SI some
quartz()
ggplot(d_all, aes(x=GQ_some_correct, y=SI_implicature, colour=Agesplit)) + 
  geom_point(stat = "identity", position = position_jitter(.001), shape=16) + 
  geom_smooth(method="lm", col="black", lty=1) + 
  geom_smooth(aes(col=Agesplit, group=Agesplit), 
				se=FALSE, method="lm",lty=3) + 
  scale_colour_brewer(palette="Set1") + 
  labs(y = "Proportion of SI 'implicature' trials correct", x = "Proportion of GQ 'some' trials correct")

#GQ some and SI implicatures
quartz()
qplot(GQ_some_correct, SI_implicature, col=Agesplit, 
	ylab="Proportion of SI 'implicature' trials correct",
	xlab="Proportion of GQ 'some' trials correct",
		position=position_jitter(.0086), data=d_all) + 
	geom_smooth(method="lm", col="black", lty=1) + 
			theme_bw()+
	geom_smooth(aes(col=Agesplit, group=Agesplit), 
				se=FALSE, method="lm",lty=3)

#SI none with GQ none
quartz()
ggplot(d_all, aes(x=GQ_none_correct, y=SI_none, colour=Agesplit)) + 
  geom_point(stat = "identity", position = position_jitter(.001), shape=16) + 
  geom_smooth(method="lm", col="black", lty=1) + 
  geom_smooth(aes(col=Agesplit, group=Agesplit), 
				se=FALSE, method="lm",lty=3) + 
  scale_colour_brewer(palette="Set1") + 
  labs(y = "Proportion of SI 'none' trials correct", x = "Proportion of GQ 'none' trials correct")

```

Linear Models

Try predicting none on the basis of control.

```{r}
summary(glm(SI_none ~  DCCS_post, data=d_all, 
            family = "binomial"))
summary(glm(GQ_none_correct == 0 ~  DCCS_post, data=d_all, 
            family = "binomial"))
summary(glm(GQ_none_correct == 0 ~  DCCS_post + test_age, data=d_all, 
            family = "binomial"))
```

Try predicting some on the basis of control
```{r}
summary(glm(GQ_some_correct ~  DCCS_post + test_age, data=d_all, 
            family = "binomial"))
```

Try predicting SI by GQ
```{r}
summary(glm(SI_implicature ~  GQ_some_correct, data=d_all, 
            family = "binomial"))
summary(glm(GQ_some_correct ~  GQ_some_correct + test_age, data=d_all, 
            family = "binomial"))
summary(glm(SI_none ~  GQ_none_correct, data=d_all, 
            family = "binomial"))
summary(glm(SI_none ~  GQ_none_correct + test_age, data=d_all, 
            family = "binomial"))
summary(glm(SI_implicature ~  GQ_none_correct, data=d_all, 
            family = "binomial"))
summary(glm(SI_implicature ~  GQ_none_correct + test_age, data=d_all, 
            family = "binomial"))
```

